Diamond exploration
=====================

```{r}
diamonds = read.csv('diamonds.csv') 
```


Import the data


```{r}
library(ggplot2) 
data(diamonds)

?diamonds
summary(diamonds)
```


# Create a histogram of the price of
# all the diamonds in the diamond data set.

# TYPE YOUR CODE BELOW THE LINE
# =======================================

```{r}

qplot(x = price, data = diamonds, binwidth = 500)
```

```{r}
sum(diamonds$price < 500)
sum(diamonds$price < 250)
sum(diamonds$price >= 15000)

```

# Explore the largest peak in the
# price histogram you created earlier.

# Try limiting the x-axis, altering the bin width,
# and setting different breaks on the x-axis.

# There won't be a solution video for this
# question so go to the discussions to
# share your thoughts and discover
# what other people find.

# You can save images by using the ggsave() command.
# ggsave() will save the last plot created.
# For example...
#                  qplot(x = price, data = diamonds)
#                  ggsave('priceHistogram.png')

# ggsave currently recognises the extensions eps/ps, tex (pictex),
# pdf, jpeg, tiff, png, bmp, svg and wmf (windows only).

# Submit your final code when you are ready.

# TYPE YOUR CODE BELOW THE LINE
# ======================================================================

```{r}
qplot(x = price, data = diamonds, binwidth = 10)

qplot(x = price, data = diamonds, binwidth = 1) +
  scale_x_continuous(limits = c(250,500))


```

# Break out the histogram of diamond prices by cut.

# You should have five histograms in separate
# panels on your resulting plot.

# TYPE YOUR CODE BELOW THE LINE
# ======================================================

```{r}
qplot(x = price, data = subset(diamonds, !is.na(cut)), binwidth = 10) +
 facet_wrap(~cut)
  
subset(diamonds,diamonds$price == max(diamonds$price))
subset(diamonds,diamonds$price == min(diamonds$price))

table(diamonds$cut)
by(diamonds$price, diamonds$cut, summary)





# In the two last exercises, we looked at
# the distribution for diamonds by cut.

# Run the code below in R Studio to generate
# the histogram as a reminder.

# ===============================================================

qplot(x = price, data = diamonds) + facet_wrap(~cut, scales = "free")
                                                                               
# ===============================================================

# In the last exercise, we looked at the summary statistics
# for diamond price by cut. If we look at the output table, the
# the median and quartiles are reasonably close to each other.

# diamonds$cut: Fair
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#     337    2050    3282    4359    5206   18570 
# ------------------------------------------------------------------------ 
# diamonds$cut: Good
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#     327    1145    3050    3929    5028   18790 
# ------------------------------------------------------------------------ 
# diamonds$cut: Very Good
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#     336     912    2648    3982    5373   18820 
# ------------------------------------------------------------------------ 
# diamonds$cut: Premium
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#     326    1046    3185    4584    6296   18820 
# ------------------------------------------------------------------------ 
# diamonds$cut: Ideal
#    Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
#     326     878    1810    3458    4678   18810 

# This means the distributions should be somewhat similar,
# but the histograms we created don't show that.

# The 'Fair' and 'Good' diamonds appear to have 
# different distributions compared to the better
# cut diamonds. They seem somewhat uniform
# on the left with long tails on the right.

# Let's look in to this more.

# Look up the documentation for facet_wrap in R Studio.
# Then, scroll back up and add a parameter to facet_wrap so that
# the y-axis in the histograms is not fixed. You want the y-axis to
# be different for each histogram.

# If you want a hint, check out the Instructor Notes.



# Create a histogram of price per carat
# and facet it by cut. You can make adjustments
# to the code from the previous exercise to get
# started.

# Adjust the bin width and transform the scale
# of the x-axis using log10.

# Submit your final code when you are ready.

# ENTER YOUR CODE BELOW THIS LINE.
# ===========================================================================
qplot(x = log10(price), data = diamonds) +
      scale_x_log10() +
      facet_wrap(~cut, scales = "free")
  

# Investigate the price of diamonds using box plots,
# numerical summaries, and one of the following categorical
# variables: cut, clarity, or color.

# There won't be a solution video for this
# exercise so go to the discussion thread for either
# BOXPLOTS BY CLARITY, BOXPLOT BY COLOR, or BOXPLOTS BY CUT
# to share you thoughts and to
# see what other people found.

# =================================================================
qplot(x = clarity, y = price, 
      data = subset(diamonds, !is.na(clarity)),
      geom = 'boxplot') + 
      scale_y_continuous(limits = c(0,6000))



table(diamonds$color)
by(diamonds$price, diamonds$color, summary)


IQR(subset(diamonds, diamonds$color == 'D')$price)
IQR(subset(diamonds, diamonds$color == 'J')$price)


# Investigate the price per carat of diamonds across
# the different colors of diamonds using boxplots.

# SUBMIT YOUR CODE BELOW THIS LINE
# ===================================================================
qplot(x = color, y = price, 
      data = subset(diamonds, !is.na(color)),
      geom = 'boxplot') + 
      scale_y_continuous(limits = c(0,5000))


# Frequency polygon

qplot(x = carat, data = subset(diamonds,!is.na(carat)), binwidth = 0.1, 
      xlab = 'Weight in Carats',
      ylab = 'Count of diamond with that carat',
      geom = 'freqpoly', color = carat) +
      scale_x_continuous(limits = c(1,2), breaks = seq(1,2,0.1)) +
      scale_y_continuous(breaks = seq(0,10000,2000))
#      scale_x_log10()


# The Gapminder website contains over 500 data sets with information about
# the world's population. Your task is to download a data set of your choice
# and create 2-5 plots that make use of the techniques from Lesson 3.

# You might use a simple histogram, a boxplot split over a categorical variable,
# or a frequency polygon. The choice is yours!

# You can find a link to the Gapminder website in the Instructor Notes.

# Once you've completed your investigation, create a post in the discussions that includes:
#       1. any questions you answered, your observations, and summary statistics
#       2. snippets of code that created the plots
#       3. links to the images of your plots

# You can save images by using the ggsave() command.

# ====================================================================================





```