Diamond exploration
=====================

```{r}
diamonds = read.csv('diamonds.csv') 
```


Import the data


```{r}
library(ggplot2) 
data(diamonds)

?diamonds
summary(diamonds)
```


# Create a histogram of the price of
# all the diamonds in the diamond data set.

# TYPE YOUR CODE BELOW THE LINE
# =======================================

```{r}

qplot(x = price, data = diamonds, binwidth = 500)
```

```{r}
sum(diamonds$price < 500)
sum(diamonds$price < 250)
sum(diamonds$price >= 15000)

```

# Explore the largest peak in the
# price histogram you created earlier.

# Try limiting the x-axis, altering the bin width,
# and setting different breaks on the x-axis.

# There won't be a solution video for this
# question so go to the discussions to
# share your thoughts and discover
# what other people find.

# You can save images by using the ggsave() command.
# ggsave() will save the last plot created.
# For example...
#                  qplot(x = price, data = diamonds)
#                  ggsave('priceHistogram.png')

# ggsave currently recognises the extensions eps/ps, tex (pictex),
# pdf, jpeg, tiff, png, bmp, svg and wmf (windows only).

# Submit your final code when you are ready.

# TYPE YOUR CODE BELOW THE LINE
# ======================================================================

```{r}
qplot(x = price, data = diamonds, binwidth = 10)

qplot(x = price, data = diamonds, binwidth = 1) +
  scale_x_continuous(limits = c(250,500))


```

# Break out the histogram of diamond prices by cut.

# You should have five histograms in separate
# panels on your resulting plot.

# TYPE YOUR CODE BELOW THE LINE
# ======================================================

```{r}
qplot(x = price, data = subset(diamonds, !is.na(cut)), binwidth = 10) +
 facet_wrap(~cut)
  
subset(diamonds,diamonds$price == max(diamonds$price))
subset(diamonds,diamonds$price == min(diamonds$price))

table(diamonds$cut)
by(diamonds$price, diamonds$cut, summary)

```