# Create a histogram of diamond prices.
# Facet the histogram by diamond color
# and use cut to color the histogram bars.

# The plot should look something like this.
# http://i.imgur.com/b5xyrOu.jpg

# Note: In the link, a color palette of type
# 'qual' was used to color the histogram using
# scale_fill_brewer(type = 'qual')

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ===========================================

```{r}
library(ggplot2)

diamonds = read.csv('diamonds.csv')
data(diamonds)

head(diamonds)

ggplot(aes(price), data = diamonds) +
  geom_histogram() +
  facet_wrap(~color, ncol = 3)

```
# Create a scatterplot of diamond price vs.
# table and color the points by the cut of
# the diamond.

# The plot should look something like this.
# http://i.imgur.com/rQF9jQr.jpg

# Note: In the link, a color palette of type
# 'qual' was used to color the scatterplot using
# scale_color_brewer(type = 'qual')

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ===========================================


```{r}

ggplot(aes(table,price), data = diamonds) +
  geom_point(aes(color = cut)) +
  xlim(c(50,80))

```

# Create a scatterplot of diamond price vs.
# volume (x * y * z) and color the points by
# the clarity of diamonds. Use scale on the y-axis
# to take the log10 of price. You should also
# omit the top 1% of diamond volumes from the plot.

# Note: Volume is a very rough approximation of
# a diamond's actual volume.

# The plot should look something like this.
# http://i.imgur.com/excUpea.jpg

# Note: In the link, a color palette of type
# 'div' was used to color the scatterplot using
# scale_color_brewer(type = 'div')

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ===========================================


```{r}


ggplot(aes(x*y*z, price), data = subset(diamonds, !is.na(price))) +
  geom_point(aes(color = clarity)) +
  scale_y_log10() +
  xlim(c(0,300)) +
  xlab('Volume')
```

# Many interesting variables are derived from two or more others.
# For example, we might wonder how much of a person's network on
# a service like Facebook the user actively initiated. Two users
# with the same degree (or number of friends) might be very
# different if one initiated most of those connections on the
# service, while the other initiated very few. So it could be
# useful to consider this proportion of existing friendships that
# the user initiated. This might be a good predictor of how active
# a user is compared with their peers, or other traits, such as
# personality (i.e., is this person an extrovert?).

# Your task is to create a new variable called 'prop_initiated'
# in the Pseudo-Facebook data set. The variable should contain
# the proportion of friendships that the user initiated.

# This programming assignment WILL BE automatically graded.

# ENTER YOUR CODE BELOW THIS LINE
# ========================================================================
```{r}

pf = read.csv('pseudo_facebook.tsv', sep = '\t')
pf$prop_initiated = with(pf, friendships_initiated/friend_count)
summary(pf$prop_initiated)

```

# Create a line graph of the median proportion of
# friendships initiated ('prop_initiated') vs.
# tenure and color the line segment by
# year_joined.bucket.

# Recall, we created year_joined.bucket in Lesson 5
# by first creating year_joined from the variable tenure.
# Then, we used the cut function on year_joined to create
# four bins or cohorts of users.

# (2004, 2009]
# (2009, 2011]
# (2011, 2012]
# (2012, 2014]

# The plot should look something like this.
# http://i.imgur.com/vNjPtDh.jpg
# OR this
# http://i.imgur.com/IBN1ufQ.jpg

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ===========================================================


```{r}
pf$year_joined = floor(2014 - pf$tenure/365)
table(pf$year_joined)
pf$year_joined.bucket = cut(pf$year_joined,
                            c(2004,2009, 2011, 2012, 2014))

ggplot(aes(tenure, prop_initiated), 
        data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket), 
            stat = 'summary', fun.y= median) 

```

# Smooth the last plot you created of
# of prop_initiated vs tenure colored by
# year_joined.bucket. You can bin together ranges
# of tenure or add a smoother to the plot.

# There won't be a solution image for this exercise.
# You will answer some questions about your plot in
# the next two exercises.

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ====================================================

```{r}

ggplot(aes(7 * round(tenure / 7), prop_initiated), 
        data = subset(pf, !is.na(year_joined.bucket))) + 
  geom_line(aes(color = year_joined.bucket), 
            stat = 'summary', fun.y= median)

library(dplyr)

  pf %>% 
  filter(year_joined.bucket == 4) %>%
  summarise(mean_friend_count = mean(friend_count),
          median_friend_count = median(friend_count),
          n = n())

  pf %>% 
  filter(year_joined.bucket == '(2012,2014]' & !is.na(prop_initiated)) %>%
  summarise(mean(prop_initiated))

```

# Create a scatter plot of the price/carat ratio
# of diamonds. The variable x should be
# assigned to cut. The points should be colored
# by diamond color, and the plot should be
# faceted by clarity.

# The plot should look something like this.
# http://i.imgur.com/YzbWkHT.jpg.

# Note: In the link, a color palette of type
# 'div' was used to color the histogram using
# scale_color_brewer(type = 'div')

# This assignment is not graded and
# will be marked as correct when you submit.

# ENTER YOUR CODE BELOW THIS LINE
# ===========================================

```{r}

ggplot(aes(cut, price/carat), data = diamonds) +
  geom_jitter(aes(alpha = 1/4,color = color)) +
  facet_wrap(~clarity, ncol = 3)






```
